---
title: Whole embryo HDCA - plotting ST
author: Raphaël Mauron
output: html_document
editor_options: 
  chunk_output_type: console
---

# HDCA - Whole Embryo Project

## Set up

### Set project library

```{r setup, include=FALSE}
#.libPaths("/home/rstudio/renv/library/R-4.3/aarch64-unknown-linux-gnu/")
.libPaths("/home/rstudio/.cache/R/renv/sandbox/R-4.3/aarch64-unknown-linux-gnu/25ebdc09")

lapply(.libPaths()[1], list.files) # check library

knitr::opts_chunk$set(echo = TRUE) # plot when knitting

rm(list = ls()) # empty object loaded
```


### Load library

```{r}
package.list <- c("semla", "Seurat", "viridis", "dplyr", "ggplot2", "gtools", "patchwork",
                  "RColorBrewer")
invisible(lapply(package.list, function(element) {
  library(element, character.only = TRUE)
}))
rm(package.list)
```


### Set directory

```{r}
setwd("/home/rstudio")
getwd()
savepath <- "./results/"
```


### You can organize how to save plots

```{r}
# create plot.directory for each section
plot.dir <- paste0(c(savepath, "save-plot"), collapse = "/")
if (dir.exists(plot.dir)) {
} else {
  dir.create(plot.dir, recursive = TRUE)
}
```


### Set seed for project

```{r}
set.seed(1)
```


### Load objects

```{r}
section_cluster <- readRDS(paste0("section_cluster_list_obj", ".rds"))
```


### Plotting

#### 1. Select embryo section

"XDD410-section-152"   "XDD410-section-162"   "XDD410-section-173"  
"XDD410-section-188"   "XDD421-section-8"     "XDD421-section-20-31"
"XDD421-section-41"    "XDD421-section-53"    "XDD421-section-63"   
"XDD421-section-74"    "XDD421-section-86"    "XDD421-section-98"   
"XDD469-section-94"    "XDD469-section-105"   "XDD419-section-37"   
"XDD419-section-46"    "XDD469-section-13"    "XDD469-section-34"   
"XDD469-section-52"    "XDD469-section-76"    "XDD410-section-200"  
"XDD410-section-213"   "XDD410-section-226"   "XDD410-section-238"  


```{r}
# change here
embryo_section <- "XDD410-section-152"
```

```{r}
object  <- section_cluster[[embryo_section]]
```


#### 2. Plot a gene onto the section

```{r}
# change here
gene_of_interest <- "MYH6"

p <- MapFeatures(object,
            features = gene_of_interest,
            image_use = "raw",
            pt_size = 1.7
          )  &
  labs(title = embryo_section)
p
```

```{r}
#save plot
pdf(paste0(plot.dir, "/", embryo_section, "_feature_plot_", "gene_of_interest", ".pdf"), width = 10, height = 10)
print(p)
dev.off()
```


#### 3. Plot a list of genes, side by side

```{r}
# change here
list_of_genes <- c("CXCL12", "PKDCC", "GASK1B")

p <- MapFeatures(object,
            features = list_of_genes,
            image_use = "raw", # set to NULL if you don't want the overlap with H&E
            pt_size = 0.8
          )  &
  labs(title = embryo_section)
p
```

```{r}
#save plot
# NOTE: you can change saving dimentions in case the dots are to big or too small
pdf(paste0(plot.dir, "/", embryo_section, "_feature_plot_", paste(list_of_genes, collapse = "_"), ".pdf"), width = 10, height = 10)
print(p)
dev.off()
```


#### 4. Plot cluster 

##### All together

```{r}
p <- MapLabels(object,
          column_name = "seurat_clusters",
          ncol = 1,
          pt_size = 1.7) &
  theme(legend.position = "right")  &
  labs(title = paste0("Clusters on ", embryo_section))
p
```

```{r}
#save plot
pdf(paste0(plot.dir, "/", embryo_section, "_all_clusters", ".pdf"), width = 10, height = 10)
print(p)
dev.off()
```


##### 1 plot per cluster

```{r}
# Plot clusters in split view
p <- MapLabels(object, column_name = "seurat_clusters", pt_size = 0.8, split_labels = TRUE, ncol = 4) & 
  labs(title = embryo_section)
p
```

```{r}
#save plot
pdf(paste0(plot.dir, "/", embryo_section, "_individual_clusters", ".pdf"), width = 10, height = 15)
print(p)
dev.off()
```

```{r}
sessionInfo()
```

